Bird beak's elaboration and innovation

### 2022-05-20 Analysis/06-Figure3_with_correlations.Rmd
Update 06-Figure3_with_correlations.Rmd

```{r, echo = FALSE, eval = FALSE}
library(ggplot2)
## Getting the data to plot
global_data <- super_phylo_cor$phylogeny

gg.density.plot <- function(data, palette = "viridis") {
    ggplot(data.frame("elaboration" = data$x, "exploration" = data$y), aes(x=elaboration, y=exploration) ) +
      geom_hex() +
      scale_fill_continuous(type = palette) +
      theme_bw()
}

pdf("../Manuscript/Figures/Figure3_b.pdf", height = 4, width = 4)
gg.density.plot(global_data)
dev.off()
```

@@

pdf("../Manuscript/Figures/Figure3_cd.pdf", height = 12, width = 8)
## Great the plot layout
layout_matrix <- cbind(matrix(0,2,2), matrix(0,2,2))
layout_matrix <- rbind(rbind(layout_matrix, matrix(1:8, 2, 4, byrow = TRUE)), matrix(9:16, 2, 4,  byrow = TRUE))
plot_layout <- layout(layout_matrix)
# layout.show(plot_layout)
one.plot.correlations <- function(cor.results, col.sub, col.fun = colour.palette, legend.pos = "topleft", pt.cex = 0.5, legend.cex = 0.5, ID, legend_counter, contour = NULL) {

@@

@@

for(i in 1:8) {
    par(mar = c(2,2.5,2,1.5))
    one.plot.correlations(super_phylo_cor[[i]], col.sub = col_subs[[i]], legend.pos = legends_pos[i], ID = i, pt.cex = 0.5, legend.cex = 2/3, legend_counter = legend_counter, contour = centroids)
}

@@

for(i in 1:8) {
    par(mar = c(2,2.5,2,1.5))
    one.plot.correlations(super_group_cor[[i]], col.sub = col_subs[[i]], legend.pos = legends_pos[i], ID = i, pt.cex = 0.5, legend.cex = 2/3, legend_counter = legend_counter)
}
dev.off()
```

>>>>

```{r, echo = FALSE, eval = FALSE}
pdf("../Manuscript/Figures/Figure3_b.pdf", height = 4.5, width = 4)

data <- super_phylo_cor$phylogeny
scale.rgb <- function(x, y, max.x, max.y, alpha = 1) {
    return(rgb(red = 255-((x/max.x)*255), blue = 255-((y/max.y)*255), green = 255, maxColorValue = 255, alpha = alpha*255))
}
add.quadrant <- function(data) {
    max.x = max(range(pretty(data$x)))
    max.y = max(range(pretty(data$y)))

    ## Bottom left
    polygon(x = c(0, 0, mean(range(pretty(data$x))), mean(range(pretty(data$x)))),
            y = c(0, mean(range(pretty(data$y))), mean(range(pretty(data$y))), 0),
            col = scale.rgb(0, 0, max.x, max.y, alpha = 1/3), border = "white")
    ## Bottom right
    polygon(x = c(mean(range(pretty(data$x))), mean(range(pretty(data$x))), max(range(pretty(data$x))), max(range(pretty(data$x)))),
            y = c(0, mean(range(pretty(data$y))), mean(range(pretty(data$y))), 0),
            col = scale.rgb(max(range(pretty(data$x))), 0, max.x, max.y, alpha = 1/3), border = "white")
    ## Top left
    polygon(x = c(0, 0, mean(range(pretty(data$x))), mean(range(pretty(data$x)))),
            y = c(mean(range(pretty(data$y))), max(range(pretty(data$y))), max(range(pretty(data$y))), mean(range(pretty(data$y)))),
            col = scale.rgb(0, max(range(pretty(data$y))), max.x, max.y, alpha = 1/3), border = "white")
    ## Top right
    polygon(x = c(mean(range(pretty(data$x))), mean(range(pretty(data$x))), max(range(pretty(data$x))), max(range(pretty(data$x)))),
            y = c(mean(range(pretty(data$y))), max(range(pretty(data$y))), max(range(pretty(data$y))), mean(range(pretty(data$y)))),
            col = scale.rgb(max(range(pretty(data$x))), max(range(pretty(data$y))), max.x, max.y, alpha = 1/3), border = "white")

    abline(v = mean(range(pretty(data$x))), lwd = 0.5, lty = 2)
    abline(h = mean(range(pretty(data$y))), lwd = 0.5, lty = 2)
}
quadrant.color <- function(elaboration, innovation, exact.color = FALSE, alpha = 1/3) {

    ## Max values (from the whole dataset)
    max.x <- 2.5
    max.y <- 1.4

    if(exact.color) {
        return(rgb(red = 255-((elaboration/max.x)*255), blue = 255-((innovation/max.y)*255), green = 255, maxColorValue = 255, alpha = alpha*255))
    }

    ## Get the position in the quadrant
    quadrant <- as.integer(c(elaboration < (max.x/2), innovation < (max.y/2)))

    ## Get the position name
    if(all(quadrant == c(1, 1))) {
        return(rgb(red = 255, blue = 255, green = 255, maxColorValue = 255, alpha = alpha*255))
    } else {
        if(all(quadrant == c(1, 0))) {
            return(rgb(red = 0, blue = 255, green = 255, maxColorValue = 255, alpha = alpha*255))
        } else {
            if(all(quadrant == c(0, 1))) {
                return(rgb(red = 255, blue = 0, green = 255, maxColorValue = 255, alpha = alpha*255))
            } else {
                if(all(quadrant == c(0, 0))) {
                    return(rgb(red = 0, blue = 0, green = 255, maxColorValue = 255, alpha = alpha*255))
                }
            }
        }
    }
}

max.x = max(range(pretty(data$x)))
max.y = max(range(pretty(data$y)))

par(mar = c(5, 4, 4, 2) + 0.1)
plot(NULL, xlab = "elaboration", ylab = "innovation", xlim = range(pretty(data$x)), ylim = range(pretty(data$y)))
add.quadrant(data)
# points(data$x, data$y, pch = 21, col = scale.rgb(data$x, data$y, max.x = max.x, max.y = max.y))
colour_densities <- densCols(cbind(data$x, data$y), colramp = scales::viridis_pal(alpha = 1, begin = 0, end = 1, direction = 1, option = "D"))
points(cbind(data$x, data$y), col = colour_densities, pch = 20)

dev.off()
```

@@

pdf("../Manuscript/Figures/Figure3_cd.pdf", height = 12, width = 8)
## Great the plot layout
layout_matrix <- cbind(matrix(0,2,2), matrix(0,2,2))
layout_matrix <- rbind(rbind(layout_matrix, matrix(1:8, 2, 4, byrow = TRUE)), matrix(9:16, 2, 4,  byrow = TRUE))
plot_layout <- layout(layout_matrix)
# layout.show(plot_layout)
one.plot.correlations <- function(cor.results, col.sub, col.fun = colour.palette, legend.pos = "topleft", pt.cex = 0.5, legend.cex = 0.5, ID, legend_counter, contour = NULL, with.quadrant = FALSE) {

@@

    if(with.quadrant) {
        add.quadrant(plot_data)
    }

@@

for(i in 1:8) {
    par(mar = c(2,2.5,2,1.5))
    one.plot.correlations(super_phylo_cor[[i]], col.sub = col_subs[[i]], legend.pos = legends_pos[i], ID = i, pt.cex = 0.5, legend.cex = 2/3, legend_counter = legend_counter, contour = NULL, with.quadrant = TRUE)
}

@@

for(i in 1:8) {
    par(mar = c(2,2.5,2,1.5))
    one.plot.correlations(super_group_cor[[i]], col.sub = col_subs[[i]], legend.pos = legends_pos[i], ID = i, pt.cex = 0.5, legend.cex = 2/3, legend_counter = legend_counter, with.quadrant = TRUE)
}
dev.off()
```
